### 2018-01-15 Atomic Spectra/paper.tex
added more data...

\paperfig{UnknownNine}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
\papertableindex\papertablecval{TODO}\papertablecval{Red}\\\paperiline
\papertableindex\papertablecval{TODO}\papertablecval{Orange}\\\paperiline
\papertableindex\papertablecval{TODO}\papertablecval{Yellow}\\\paperiline
\papertableindex\papertablecval{TODO}\papertablecval{Green}\\\paperoline
\end{papertable}\vspace{-1.5em}}
{The scale readings and colours of the spectral lines of ``Unknown \#9''.}

@@

\paperfig{ScaleFit}{\begin{tikzpicture}[scale=0.95]
\begin{axis}[width=\linewidth,
tick label style={font=\fontsize{10pt}{1em}},
xlabel={\fontsize{10pt}{1em}\selectfont $\frac{1}{\lambda-\lambda_0}$ ($10^6$ $\si{\per\meter})\rightarrow$},
ylabel={\fontsize{10pt}{1em}\selectfont $y\rightarrow$},
\paperaxis{Scale Reading vs. Modified Wavelength}{y}{x}{2}{5}{8}{15}{2}{2}]
\papergraphoutline{2}{5}{8}{15};
\addplot [color=black,only marks,mark=o,mark size=1.5,
error bars/.cd,
y dir=both,y explicit,
x dir=both,x explicit
] coordinates {
(2.374, 6.66) +- (0.002,0.02)
(2.614, 7.06) +- (0.003,0.02)
(3.307, 8.31) +- (0.004,0.02)
(4.621, 11.09) +- (0.009,0.02)
(4.831, 11.50) +- (0.009,0.02)
(5.37, 12.58) +- (0.01,0.02)
(6.18, 14.19) +- (0.02,0.02)
};
\addplot[no marks,
samples=250,
domain=2:8]
{2*x+1.83};
\end{axis}
\end{tikzpicture}}
{The scale readings on the spectrometer plotted against the modified
wavelengths with the line of best fit.
The line has a function of $(2.00\pm.02)\text{E-6}x+(1.83\pm.09)$ and an
\smash{$R^2$} value of 0.999489.
Error bars were included but were too small to be visible.}

@@

By converting all the scale readings from \figHydrogen and plugging the
wavelengths and the line indices into \eqRydberg, four approximations
for the Rydberg constant were obtained.
They were averaged to get the final value for $R_H$, which was
$(1.097\pm.003)\x\SI{E7}{\per\meter}$, which was well within the range of the
experimental error from the accepted $\SI{1.09737316E7}{\per\meter}$.

>>>>

\paperfig{UnknownNine}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
\papertableindex\papertablecval{6.61}\papertablecval{Red}\\\paperiline
\papertableindex\papertablecval{8.05}\papertablecval{Orange}\\\paperiline
\papertableindex\papertablecval{8.50}\papertablecval{Yellow}\\\paperiline
\papertableindex\papertablecval{9.65}\papertablecval{Green}\\\paperoline
\end{papertable}\vspace{-1.5em}}
{The scale readings and colours of the spectral lines of ``Unknown \#9''.}

@@

\paperfig{ScaleFit}{\begin{tikzpicture}[scale=0.95]
\begin{axis}[width=\linewidth,
tick label style={font=\fontsize{10pt}{1em}},
xlabel={\fontsize{10pt}{1em}\selectfont $\frac{1}{\lambda-\lambda_0}$ $(\SI{E6}{\per\meter})\rightarrow$},
ylabel={\fontsize{10pt}{1em}\selectfont $y\rightarrow$},
\paperaxis{Scale Reading vs. Modified Wavelength}{y}{x}{2}{5}{8}{15}{2}{2}]
\papergraphoutline{2}{5}{8}{15};
\addplot [color=black,only marks,mark=o,mark size=1.5,
error bars/.cd,
y dir=both,y explicit,
x dir=both,x explicit
] coordinates {
(2.374, 6.66) +- (0.002,0.02)
(2.614, 7.06) +- (0.003,0.02)
(3.307, 8.31) +- (0.004,0.02)
(4.621, 11.09) +- (0.009,0.02)
(4.831, 11.50) +- (0.009,0.02)
(5.37, 12.58) +- (0.01,0.02)
(6.18, 14.19) +- (0.02,0.02)
};
\addplot[no marks,
samples=250,
domain=2:8]
{2*x+1.83};
\end{axis}
\end{tikzpicture}}
{The scale readings on the spectrometer plotted against the modified
wavelengths with the line of best fit.
The line has a function of $(2.00\pm.02)\x\SI{E-6}{}x+(1.83\pm.09)$ and an
\smash{$R^2$} value of 0.999489.
Error bars were included but were too small to be visible.}

@@

By converting all the scale readings from \figHydrogen and plugging the
wavelengths and the line indices into \eqRydberg, four approximations
for the Rydberg constant were obtained.
They were averaged to get the final value for $R_H$, which was
$(1.097\pm.003)\x\SI{E7}{\per\meter}$, which was well within the range of the
experimental error from the accepted value of $\SI{1.09737316E7}{\per\meter}$.

The reversed formula was used to compute the wavelengths of the observed
spectral lines for the two unknown gases.
The following results were obtained for the two unknown gases.

\paperfig{UnknownSevenResult}{\begin{papertable}{|[outer]I|[inner]U|[inner]C|[outer]}
\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Wavelength}}&\multirow{2}{*}{\textsc{Colour}}\\
\papertableuheaderunit{\si{\nano\meter}}&\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Orange}\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Green}\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Violet}\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Violet}\\\paperoline
\end{papertable}\vspace{-1.5em}}
{The wavelengths and colours of the spectral lines of ``Unknown \#7''.}\vspace{1em}

\paperfig{UnknownNineResult}{\begin{papertable}{|[outer]I|[inner]U|[inner]C|[outer]}
\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Wavelength}}&\multirow{2}{*}{\textsc{Colour}}\\
\papertableuheaderunit{\si{\nano\meter}}&\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Red}\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Orange}\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Yellow}\\\paperiline
\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Green}\\\paperoline
\end{papertable}\vspace{-1.5em}}
{The wavelengths and colours of the spectral lines of ``Unknown \#9''.}
